Learning Network Size while Training with ShrinkNets

### 2018-02-09 paper/ICML/evaluation.tex
Make a statement less strong

On the plot, the Pareto front for the two training methods clearly indicates
that not only \textit{ShrinkNets} find models that are as accurate as
\textit{Static Networks}, but they are more efficient in terms of size. Even
when we sample the entire size space (in the \texttt{COVERTYPE} case),
\textit{ShrinkNets} are better or equally as good as \textit{Static Networks}.
it has two implications. First it reinforces, our observation in [ref] that
showed that the models do not suffer from the non-convexity introduced by the
multiplication by the \textit{Switch Layer}. Secondly it could let us conjecture
that the parametrization from a $\lambda$ (real value) to the size of the
size of the network (vector) is optimal or close to optimal. Indeed, if it was
not the case then eventually a randomly sampled size would have beaten
\textit{ShrinkNets} models. \gl{Too strong ?}

>>>>

On the plot, the Pareto front for the two training methods clearly indicates
that not only \textit{ShrinkNets} find models that are as accurate as
\textit{Static Networks}, but they are more efficient in terms of size. Even
when we sample the entire size space (in the \texttt{COVERTYPE} case),
\textit{ShrinkNets} are better or equally as good as \textit{Static Networks}.
it has two implications. First it reinforces, our observation in [ref] that
showed that the models do not suffer from the non-convexity introduced by the
multiplication by the \textit{Switch Layer}. Secondly it could let us conjecture
that the parametrization from a $\lambda$ (real value) to the size of the
size of the network (vector) close to optimal. Indeed, if it was
not the case then eventually a randomly sampled size would have beaten
\textit{ShrinkNets} models. \gl{Too strong ?}
